Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-06 minimax.tex
Table/Plot Comparison and partial Plot Linearity

\subsection{Our previous presentation}
\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} \\
			\midrule
			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
			20 & 9.05 & 0.51 & 7.38 & 0.65 & 6.08 & 0.76\\
			40 & 7.3 & 0.62 & 4.21 & 1.18 & 2.77 & 1.27\\
			60 & 6.01 & 0.81 & 1.56 &0.98 & 1.23 & 1.22\\
			80 & 4.72 & 1.07 & 0.2 & 0.33 & 0.55 & 0.71\\
			100 & 3.0 & 0.97 & 0.0 &  0.0 & 0.2 & 0.28\\
			120 & 1.31 & 1.15 & 0.0 & 0.0 & 0.1 & 0.21\\
			140 & 0.44 & 0.85 & 0.0 & 0.0 & 0.1 & 0.21\\
			150 & 0.21 & 0.58 & 0.0 & 0.0 & 0.1 & 0.21\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average minimax regret in problems of size $(5, 10)$ after $k$ questions over $25$ runs.}
	\label{fig:55}
\end{table}

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd} & {sd} & {L.\ pes.} & {sd??} \\
			\midrule
			0 & 20.0 & 0.0 & 20.0 & 0.0 \\
			50 & 19.81 & 0.12 & 17.19 & 1.2 \\
			100 & 19.22 & 0.25 & 14.72 & 2.4 \\
			150 & 18.18 & 0.54 & 12.52 & 3.89 \\
			200 & 17.05  & 0.29 & 10.57 & 5.14 \\
			250 & 15.95 & 0.26 & 9.28 & 6.17 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average regret in problems of size $(10, 20)$ after $k$ questions over $5$ runs.}
	\label{fig:1020}
\end{table}

@@

The results are displayed in \cref{fig:55,fig:1020,fig:p}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.

@@

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 & 5.02 & 0.82 & 3.21 & 1.6 \\
			25 & 5.83 & 1.25 & 6.79 & 1.2 \\
			50 & 6.47 & 1.14 & 5.2 & 1.58 \\
			100 & 9.4 & 1.58 & 8.66 & 0.51 \\
			150 & 11.89 & 1.1 & 12.31 & 0.96 \\
			200 & 15.64  & 0.52 & 16.12 & 1.06 \\
			250 & 20.0 & 0.0 & 20.0 & 0.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the chair.}
	\label{fig:p}
\end{table}

>>>>

\subsection{Our previous presentation}
\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
\begin{table}
	\begin{center}
		\resizebox{\columnwidth}{!}{
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rd.\tiny{$\pi=0.1$}} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} & {Eli.} & {sd} \\
			\midrule
			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
			20 & 8.07 & 0.52 & 6.17 & 0.78 & 5.85 & 0.87& 6.32 & 0.61\\
			40 & 5.26 & 0.88 & 2.98 & 0.99 & 2.57 & 1.05 & 3.37 & 0.83\\
			60 & 2.37 & 0.93 & 0.77 &0.78 & 0.67 & 0.67 & 2.33 & 1.05\\
			80 & 0.33 & 0.49 & 0.05 & 0.18 & 0.03 & 0.12 & 2.28 & 1.05\\
			100 & 0.0 & 0.02 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
			\bottomrule
		\end{tabular}
		}
	\end{center}
	\caption{Average minimax regret in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
	\label{tab:comparison}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{comparison.png}
	\caption{Plot in support of \cref{tab:comparison}}
	\label{fig:comparison}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{linearity.png}
	\caption{Average regret after $k$ questions with Limited Pessimistic strategy after 10 runs for different problem sizes.}
	\label{fig:linearity}
\end{figure}

@@

The results are displayed in \cref{tab:comparison,fig:1020,fig:p}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.

@@

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 &  &  &  &  \\
			50 &  &  &  &  \\
			100 &  &  &  &  \\
			150 &  &  & &  \\
			200 &   &  &  &  \\
			250 &  & &  &  \\
			300 &&&& \\
			350 &&&& \\
			400 &&&& \\
			450 &&&& \\
			500 &&&& \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
	\label{fig:p}
\end{table}
